Describing the C-space of asynchronous periodic task using DIT

### 2013-07-23 dit-paper_ieee.tex
style changes, typo fixes

	In this section the current description of the C-space of synchronous
	constrained systems, which has been mostly covered by \cite{george2009characterization}, is reviewed.

@@

		We consider a discrete timeline and tasks systems $\tau$ comprised of periodic concrete
		tasks with constrained deadlines on uniprocessor platforms. Each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\

@@

		Furthermore, the following notations are used:
		\begin{itemize}
			\item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
			\item $H = \operatorname{lcm}(T_0, \cdots, T_{n-1})$
			\item $O_{max} = \max (O_0, \cdots, O_{n-1})$
			\item An \emph{idle time} is an instant $t$ at which each job that arrived
			\emph{strictly} before $t$ has finished its execution.
			\item A \emph{busy period} is a time interval during which there is always
			at least one unfinished job available in the system and maximal
			with this property. Any busy period starts and ends
			with an idle time.
			\item The interval between the initial time and the first
			idle time is called the \emph{first busy period}.
		\end{itemize}

@@

	\begin{definition}
		The \textbf{demand-bound function (DBF)}
		defined for a task set $\tau$ and noted $\dbf{t_1, t_2}$, is equal to
		the maximal cumulated execution time of jobs of $\tau$ contained in the
		closed interval $[t_1, t_2]$.
	\end{definition}

@@

			A region of $\mathbb{N}^n$ can be described by a list of parametric linear equations describing the convex hull of the admissible points. In other words, a list of conditions which can unequivocally decide if a point is included in the region or not.\\

			For the synchronous case, the DBF test gives us a list of equations which, taken together, are a necessary and sufficient condition of feasibility. Those are:
			$$\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2$$
			Note that for a given $t$, we have that the $n_i(t)$ are constant (w.r.t. the $C_i$). Those equations are thus indeed linear.\\

			However, this description contains an infinite number of equations, most of which are redundant. While this does not harm the precision of the description, an more efficient description is preferred as it can greatly reduce computation times. The next section gives a method to reduce the size of the description.

@@

\begin{remark} (from the definition):
	\begin{itemize}
		\item Contrary to the idle times, the DITs are independent of the scheduling or the execution times of the jobs.
		\item In feasible system, every DIT is an idle time.
		\item In feasible system, the first DIT happens after the end of the busy period.
		\item As $H$ is always a DIT, we have $t_d \leq H$.
	\end{itemize}
\end{remark}

Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously. Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to only consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\

To summarize, we reduced the description of the C-space from an infinite number of equations to only the equations where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job. Note that this is still exponential in the number of tasks.

@@

\begin{figure}[h]
$$
\begin{array}{|c|c|c|c|l}
   \text{Incomplete} & \text{Transitive} & \text{Stationary} & \text{$2^{nd}$ Stationary} & \cdots \\
   \text{period} & \text{period} & \text{period} & \text{period} & \\
  \hline
  t > 0 & O_{max} & O_{max} + H & O_{max} + 2H & \cdots
\end{array}
$$
\begin{center}
\caption{Behavior of an asynchronous system under EDF.}
\label{fig:asyncBehavior}
\end{center}
\end{figure}

>>>>

	In this section the current description of the C-space of synchronous
	constrained systems is reviewed, mostly through
	\cite{george2009characterization}.

@@

		We consider a discrete timeline and systems comprised of periodic concrete
		tasks with constrained deadlines on uniprocessor platforms, where each task
		$\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value,
		$C_i$ the WCET, $D_i$ the relative deadline and $T_i$ the period.
		The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In
		the following, we differentiate between \emph{synchronous systems} (where $O_i
		= 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\

@@

		Furthermore, the following notations are used:
		\begin{itemize}
			\item $\tau = \{\tau_0, \cdots, \tau_{n-1}\}$
			\item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
			\item $O_{max} = \max (O_0, \cdots, O_{n-1})$
			\item An \emph{idle time} is an instant $t$ at which each job that arrived
			\emph{strictly} before $t$ has finished its execution.
			\item A \emph{busy period} is a time interval during which there is always
			at least one job available and not finished in the system and maximal
			(in interval length) with this property. Any busy period starts and ends
			with an idle time.
			\item The interval between the initial time and the first
			idle time is called the \emph{first busy period}.
		\end{itemize}

@@

	\begin{definition}
		The \textbf{demand-bound function (DBF)}
		\cite{baruah1999generalized, baruah1990algorithms} defined for a task set
		$\tau$ and noted $\dbf{t_1, t_2}$, is equal to the maximal cumulated execution
		time of jobs of $\tau$ contained in the closed interval $[t_1, t_2]$.
	\end{definition}

@@

			A region of $\mathbb{N}^n$ can be described by a list of parametric linear
			constraints describing the convex hull of that region. In other words, a
			list of conditions which can unequivocally decide if a point is included in the region or not.\\

			For the synchronous case, the DBF test gives us a list of inequations
			on the WCET values of the task set which together are a necessary and
			sufficient condition of feasibility. They can all be written in the
			following way:
			\[
				\sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq
				t_1 \leq t_2
			\]
			Note that for a given $t$, we have that the $n_i(t)$ are
			constant (w.r.t. the $C_i$). Those equations are thus indeed linear.\\

			However, this description contains an infinite number of equations, most of
			which are redundant. While this does not harm the precision of the
			test, the smallest description is preferred as it can greatly
			reduce the computation time of practical feasibility tests using this system
			of constraints. In Section~\ref{sct:removeRedundancy} a method to reduce the size of this set of inequations is given.

	\subsection{Removing redundancy}
		\label{sct:removeRedundancy}

@@

	\begin{remark} (from the definition):
		\begin{itemize}
			\item Contrary to other idle times, DITs are independent of the
			scheduling or the execution times of the jobs.
			\item In a feasible system, every DIT is an idle time.
			\item In a feasible system, the first DIT happens after the end of the
			first busy period.
			\item As $H$ is always a DIT in synchronous systems, we have $t_d \leq H$ in
			this case.
		\end{itemize}
	\end{remark}

	Every DIT being an idle instant, the execution of the system after a DIT does
	not depend on what happened before. Because the synchronous arrival pattern is
	the worst case [citation needed], it is sufficient for the DBF test to only consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\

	To summarize, we reduced the description of the C-space from an infinite number
	of constraints to only the inequations where $t_1 = 0$, $t_2 \leqslant t_d$ and
	values of $t_2$ correspond to job deadlines. Note that the number of
	constraints is still exponential in the number of tasks.

@@

\begin{figure}[h]
\[
	\begin{array}{|c|c|c|c|l}
		\text{Incomplete} & \text{Transitive} & \text{Stationary} & 2^{nd}
		\text{Stationary} & \cdots \\
		\text{period} & \text{period} & \text{period} & \text{period} & \\
		\hline
		t > 0 & O_{max} & O_{max} + H & O_{max} + 2H & \cdots
	\end{array}
\]
\begin{center}
\caption{Behavior of an asynchronous system under EDF.}
\label{fig:asyncBehavior}
\end{center}
\end{figure}
